International Relations are a Social Network:\\ A Latent Network Approach for Global Politics

### 2017-10-19 paper/4_app.tex
fast getun

\section{Replications}

@@

\begin{table}
\caption{Features of the Studies Replicated. }
	\begin{tabular}{lcccccc}
& Model &  N. Actors  & N. Dyads & Dyads Type & Clustering $\sigma_{\hat{\beta}}$ \\ \toprule
Reiter \& Stam (2003) & Logit & 193 & $753,456$ & Directed & Robust \\	
McDonald (2004) & Logit & 198 & $92,354$ & Undirected & Robust\\
Rose (2004) & OLS & 177 & $234,597$ & Directed & Robust \\	 
Weeks (2012) & Logit & 197 &  $901,540$ & Directed & Robust \\
Gibler (2017) & Logit & 193 &    & $650,557$ & UnDirected & none \\ \bottomrule
	\end{tabular}
\end{table}

@@

%%% TO HERE
\subsection{Replication of Weeks (2012)}

The replication of \citet{weeks:2012} likely has the sharpest divergence between the General Linear Model results and those of the AME Model. In Weeks's initial models,  she finds that machines are less prone to initiate conflict than the reference category, whereas Juntas, Bosses and Strong-men are more conflict-prone, in line with her theoretical expectations. When we look at the posterior distribution of these coefficients in the AME results, we find that none of these values are distinguishable from zero. We similarly find less pronounced effects for military capabilities. One explanation for this divergence is the AME model's ability to account for third order effects. Inspection of the multiplicative effects in Figure~\ref{fig:weekscirc} reveals a number of clusters of states which exhibit structural equivalence -- in the top right corner we see states like the US, the UK, and Israel who often send conflict to similar targets. In particular, we observe a cluster of ``rogue states,'' who are receivers of conflict, in the top right (Iran, Iraq, Syria, Libya, North Korea). In the bottom corner we see a cluster of authoritarian senders including Iraq, Russia, Syria, North Korea and China. In general, these clusters have similar governmental types (Iraq, Syria, Libya, and North Korea all fell under the ``boss" category), and similar conflict behavior. So, in the GLM, which ignores these third order dependencies, much of these results might have been attributed to regime type. The AME model, on the other hand, finds that it is more efficient to attribute this behavior to the multiplicative effects. In terms of out of sample performance, shown in Figure~\ref{fig:weeksauc}, the AME model performs markedly better than the GLM out of sample, lending credence to the possibility that these third order dependencies cause spurious effects for regime type.

@@

In the original model, the variable ``Pers/Democ Directed Dyad" (which represents a Personalist $\rightarrow$ Democractic directed dyad) is clearly positive while the variable ``Democ/Personalist Directed Dyad'' is zero and the difference between the two coefficients is clearly distinct from zero. In our replication using the AME framework, we also find that Pers-Democ directed dyad has a positive effect with zero excluded from the 95\% confidence interval while Democ-Pers directed dyad is indistinguishable from zero. Using this model, however, we can no longer conclusively say that the Pers/Democratic coefficient is larger than the Democ/Personalist one.
Our replication using the AME approach therefore cast some doubt on Reiter \& Stam's key claim that MIDs initiated by personalist dictatorships against democracies are more likely than MIDS initiated by democracies. Further, the effect of most of the covariates in the literature thought to predict interstate MIDs are much closer to zero when using the AME framework. Finally, our modeling approach outperforms the original model by better, and more accurately, predicting MIDs out-of-sample (Figure~\ref{fig:reitaucpr} and Figure ~\ref{fig:reitpr}).

@@

@@

\newpage
\subsection{Replication of McDonald (2004)}

% TO DO: fix bib

Our replication reveals that trade relations are highly interdependent and exhibit important patterns of transitivity.  Or, in other words, if countries $i$ and $j$ are highly dependent and countries $j$ and $k$ are also highly dependent, then we are likely to observe high dependency between countries $i$ and $k$. Our findings support those of Traag and Lupu (2013) which argue that indirect trade relations reduce the probability of conflict. This indicates that conflict is less likely between members of a trade community. Once we control for these dependencies, we can more clearly interpret the positive link between trade and conflict. Figure~\ref{fig:mcdCoefs} shows the coefficients for both the original and AME model. The most striking thing is that AME finds a positive---not negative as found by McDonald---association between trade dependence and conflict. The AME coefficient is not only in the opposite direction, but it is approximately three times more precisely estimated.  At the same time, the AME has ROC and PR curves (not shown) that dominate the OLS results found in McDonald (2004).

@@

>>>>

\section{Re-estimation with AME}

@@

\begin{table}
\caption{Features of the Studies Re-estimated. }
	\begin{tabular}{lcccccc}
& Model &  N. Actors  & N. Dyads & Dyads Type & Clustering $\sigma_{\hat{\beta}}$ \\ \toprule
Reiter \& Stam (2003) & Logit & 193 & $753,456$ & Directed & Robust \\	
McDonald (2004) & Logit & 198 & $92,354$ & Undirected & Robust\\
Rose (2004) & OLS & 177 & $234,597$ & Directed & Robust \\	 
Weeks (2012) & Logit & 197 &  $901,540$ & Directed & Robust \\
Gibler (2017) & Logit & 193 &    & $650,557$ & UnDirected & none \\ \bottomrule
	\end{tabular}
\end{table}

@@

@@

In the original model, the variable ``Pers/Democ Directed Dyad" (which represents a Personalist $\rightarrow$ Democractic directed dyad) is clearly positive while the variable ``Democ/Personalist Directed Dyad'' is zero and the difference between the two coefficients is clearly distinct from zero. In our re-estimation using the AME framework, we also find that Pers-Democ directed dyad has a positive effect with zero excluded from the 95\% confidence interval while Democ-Pers directed dyad is indistinguishable from zero. Using this model, however, we can no longer conclusively say that the Pers/Democratic coefficient is larger than the Democ/Personalist one.
Our re-extimation using the AME approach therefore cast some doubt on Reiter \& Stam's key claim that MIDs initiated by personalist dictatorships against democracies are more likely than MIDS initiated by democracies. Further, the effect of most of the covariates in the literature thought to predict interstate MIDs are much closer to zero when using the AME framework. Finally, our modeling approach outperforms the original model by better, and more accurately, predicting MIDs out-of-sample (Figure~\ref{fig:reitaucpr} and Figure ~\ref{fig:reitpr}).

@@

\floatbarrier
\subsection{Replication of McDonald (2004)}

Our re-estimation with AME reveals that trade relations are highly interdependent and exhibit important patterns of transitivity.  Or, in other words, if countries $i$ and $j$ are highly dependent and countries $j$ and $k$ are also highly dependent, then we are likely to observe high dependency between countries $i$ and $k$. Our findings support those of Traag and Lupu (2013) which argue that indirect trade relations reduce the probability of conflict. This indicates that conflict is less likely between members of a trade community. Once we control for these dependencies, we can more clearly interpret the positive link between trade and conflict. Figure~\ref{fig:mcdCoefs} shows the coefficients for both the original and AME model. The most striking thing is that AME finds a positive---not negative as found by McDonald---association between trade dependence and conflict. The AME coefficient is not only in the opposite direction, but it is approximately three times more precisely estimated.  At the same time, the AME has ROC and PR curves (not shown) that dominate the OLS results found in McDonald (2004).

@@

\subsection{Replication of Weeks (2012)}

The re-estimation of \citet{weeks:2012} likely has the sharpest divergence between the General Linear Model results and those of the AME Model. In Weeks's initial models,  she finds that machines are less prone to initiate conflict than the reference category, whereas Juntas, Bosses and Strong-men are more conflict-prone, in line with her theoretical expectations. When we look at the posterior distribution of these coefficients in the AME results, we find that none of these values are distinguishable from zero. We similarly find less pronounced effects for military capabilities. One explanation for this divergence is the AME model's ability to account for third order effects. Inspection of the multiplicative effects in Figure~\ref{fig:weekscirc} reveals a number of clusters of states which exhibit structural equivalence -- in the top right corner we see states like the US, the UK, and Israel who often send conflict to similar targets. In particular, we observe a cluster of ``rogue states,'' who are receivers of conflict, in the top right (Iran, Iraq, Syria, Libya, North Korea). In the bottom corner we see a cluster of authoritarian senders including Iraq, Russia, Syria, North Korea and China. In general, these clusters have similar governmental types (Iraq, Syria, Libya, and North Korea all fell under the ``boss" category), and similar conflict behavior. So, in the GLM, which ignores these third order dependencies, much of these results might have been attributed to regime type. The AME model, on the other hand, finds that it is more efficient to attribute this behavior to the multiplicative effects. In terms of out of sample performance, shown in Figure~\ref{fig:weeksauc}, the AME model performs markedly better than the GLM out of sample, lending credence to the possibility that these third order dependencies cause spurious effects for regime type.

@@

\subsection{Lessons Learned from Re-estimating Five Prominent Studies}
